---
title: "Comparing models - Global"
author: "Murray Logan"
date: today
date-format: "DD/MM/YYYY"
format:
  html:
    ## Format
    theme: [default, resources/style.scss]
    css: resources/style.css
    html-math-method: mathjax
    ## Table of contents
    toc: true
    toc-float: true
    ## Numbering
    number-sections: true
    number-depth: 3
    ## Layout
    page-layout: full
    fig-caption-location: "bottom"
    fig-align: "center"
    fig-width: 4
    fig-height: 4
    out-width: 500px
    fig-dpi: 72
    tbl-cap-location: top
    ## Code
    code-fold: false
    code-tools: true
    code-summary: "Show the code"
    code-line-numbers: true
    code-block-border-left: "#ccc"
    code-copy: true
    highlight-style: atom-one
    ## Execution
    execute:
      echo: true
      #cache: true
    ## Rendering
    embed-resources: true
crossref:
  fig-title: '**Figure**'
  fig-labels: arabic
  tbl-title: '**Table**'
  tbl-labels: arabic
engine: knitr
## execute:
##   cache: true
jupyter: python3
output_dir: "docs"
documentclass: article
fontsize: 12pt
mainfont: Arial
mathfont: LiberationMono
monofont: DejaVu Sans Mono
classoption: a4paper
bibliography: resources/references.bib
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    cache.lazy = FALSE,
    tidy = "styler"
)
## allow indented chunks
assignInNamespace(".sep.label",
  "^\\ *(#|--)+\\s*(@knitr|----+)(.*?)-*\\s*$",
    ns = "knitr"
)
knitr::read_chunk("../R/process_spatial.R")
knitr::read_chunk("../R/process_benthic_data.R")
knitr::read_chunk("../R/fit_models.R")
knitr::read_chunk("../R/aggregate_models.R")
knitr::read_chunk("../R/helper_functions.R")
## knitr::read_chunk("../python/incomplete_spatial.py")
## remove the indentation from all python chunks that start
## with indentation
codes <- knitr::knit_code$get()
process_chunks <- function(codes) {
  nms <- names(codes)
  wch <- which(startsWith(names(codes), "python"))
  codes1 <- lapply(1:length(codes), function(i) {
    if (i %in% wch) {
      x <- gsub("^ {4}", "", codes[[i]])
    } else {
      x <- codes[[i]]
    }
    x
  })
  names(codes1) <- nms
  codes1
}
knitr::knit_code$set(
  process_chunks(codes)
)

options(tinytex.engine =  'xelatex')
```

```{css, echo=FALSE}
figcaption {
  text-align: left !important;
}
```

```{r}
#| label: packages
#| echo: false
#| eval: true
#| cache: false
#| warning: false
#| message: false
#| output: false
library(tidyverse)
library(kableExtra)
```

## Guide

In each of the following sections:

- the white line represents the posterior median of cover estimates
  (Bayesian Heirarchical model)
- the darkest orange band represents the 80% credibility interval of
  cover estimates (Bayesian Heirarchical model)
- the orange band represents the 95% credibility interval of the
  cover estimates (Bayesian Heirarchical model)
- the light orange band represents the 95% credibility interval of
  cover estimates for years in which there were no observed data in
  the presented spatial scale (e.g. Ecoregion, Subregion or Region)
  (Bayesian Heirarchical model).

```{r}
#| label: read aggregate global plots
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| cache: false
benthic_posteriors_global <- targets::tar_read("aggregate_global_plots_", store = "../R/_targets")
summary_global <- targets::tar_read("summary_global_", store = "../R/_targets")
summary_global_V2 <- targets::tar_read("summary_global_V2_", store = "../R/_targets")
contrasts_global <- targets::tar_read("contrasts_global_", store = "../R/_targets")
global_tbls <- targets::tar_read("global_tbls_", store = "../R/_targets")
wts_global <- targets::tar_read("wts_global_", store = "../R/_targets") 
spatial_lookup <- targets::tar_read("spatial_lookup_", store = "../R/_targets") 
```

```{r}
#| label: aggregate global plots
#| eval: true
#| echo: false
#| output: asis
#| warning: false
#| message: false
#| cache: false
## cat("::: {.panel-tabset}\n")
dat_reg <- benthic_posteriors_global 
cats <- sort(unique(dat_reg$category))
cats <- setdiff(cats, "Other fauna")
cats <- c(intersect(c("Hard coral", "Macroalgae"), cats),
          setdiff(cats, c("Hard coral", "Macroalgae")))
for (catg in cats) {
  cat(paste0("## ", catg, "\n"))
  ## Global level =====================================================================
  data_reg <- benthic_posteriors_global |>
    dplyr::filter(category == catg)
  fig <- data_reg$plot[[1]]
  fig2 <- str_replace(fig, "pdp", "pdprawxgboost")
  fig2a <- str_replace(fig, "pdp", "pdp_bayes_a_V2")

  cat("::: {.figure #fig-x}\n")
  cat(paste0("![](", fig2a,"){width=400px}\n\n"))
  cat(paste0("Modelled temporal trend (orange
  ribbon with white line) in ", catg , " with overlayed observed data
  (dots) for the Global.  The orange bands represent
  80% and 95% (darker) credibility intervals.  Grey ribbon represents 
  years for which there are no observed data.\n"))
  cat(":::\n\n")

  cat('::: {.callout-note collapse="true"}\n#### View weights\n')
  cat("::: {#tbl-wts}\n")

    wts_global |>
      dplyr::select(Region=region,
        Area=region_area,
        Weight = wt
      ) |>
    knitr::kable() |>
    print()
    cat(paste0("Region reef area and weights applied in the aggregation up to the Global scale.\n"))
    cat(":::\n")
    cat(":::\n")
    
    cat("::: {.callout-note collapse=true}\n")
    cat("#### Show data behind figure\n")
    cat("::: {#tbl-data}\n")
    summary_global_V2 |>
      filter(category == catg) |>
      _[["cellmeans_trim"]][[1]] |>
      dplyr::select(-variable) |>
      dplyr::mutate(across(c(median, lower, upper, lower_80, upper_80), \(x) round(x * 100, 2))) |>
      # knitr::kable(caption = paste0("Estimated annual ", catg, " cover (%) at the Global scale.")) |>
      knitr::kable() |>
      print()
    cat(paste0("Estimated annual ", catg, " cover (%) at the global scale.\n")) 
    cat(":::\n")
    cat(":::\n")
    
    cat("::: {.callout-note collapse=true}\n")
    cat("#### Show contrasts\n")
    cat("::: {#tbl-contr}\n")
    contrasts_global |>
      filter(category == catg) |>
      _[["contrast_sum"]][[1]] |>
      knitr::kable() |>
      print()
    cat(paste0("- ", 
      contrasts_global |>
        filter(category == catg) |>
        _[["narrative"]][[1]]$interpretation, sep="\n\n")
      )
    cat(paste0("Contrasts between pairs of years for ", catg, " cover (%) at the Global scale.
    For each contrast, results are expressed as absolute change (`abs`) and percentage 
    change (`frac`). Estimated start and end values are also presented. Negative values 
    indicate declines between the pairs of years. `Pl` and `Pg` represent the probability 
    of decline and increase respectively.\n"))
    cat(":::\n")
    cat(":::\n")

    cat("::: {#tbl-summ}\n")
    global_tbls |>
      filter(category == catg) |>
      _[["tbl"]][[1]] |>
      str_replace_all("\\.\\./\\.\\./", "../") |>
      str_replace_all("lightable-paper", "table") |>
      cat()

    cat(paste0("Change in ", catg, " cover (%) for each Region (and
       Global aggregate at the bottom) depicted as a simplified
       temporal trend as well as the direction of change (arrow)
       between a reference period (< 2010, red line on trends) and the
       2020s (blue line on trends). Values immediately to the left and
       right of the arrows represent the average cover for the
       reference and 2020s respectively.  Values in brackets represent
       the percentage change in percentage cover between the reference
       and 2020s. Weights used to aggregate from Subregion to Region
       are represented by doughnut plots with actual weights displayed
       above doughnuts. Confidence in whether there was a change in
       cover between the reference and 2020s is expressed as a signal
       strength based on Bayesian exceedence probabilities (no bars:
       Pr(Δ>0) < 0.85 (no evidence), one bar: Pr(Δ>0) < 0.90 (weak
       evidence), two bars: Pr(Δ>0) < 0.95 (evidence), three bars:
       Pr(Δ>0) < 1.00 (strong evidence), four bars Pr(Δ>0) = 1.00).
       \n"))
     cat(":::\n\n")
}
```

```{r}
#| label: aggregate global plots MA_Turf
#| eval: true
#| echo: false
#| output: asis
#| warning: false
#| message: false
#| cache: false
new_catg <- "Macroalgae and Turf algae"
catg <- "Macroalgae"
cat(paste0("## ", new_catg, "\n"))
cat("This section is simply to represent Macroalgae and 
Turf algae in the same figure. Please refer to the individual 
(above) sections on Macroalgae and Turf algae
for more detailed information.
\n\n")
  
## Global level =====================================================================
data_reg <- benthic_posteriors_global |>
  dplyr::filter(category == catg)

fig <- data_reg$plot[[1]]
fig2a <- str_replace(fig, "pdp", "pdp_bayes_a_V2")
fig2a <- str_replace(fig2a, "Macroalgae", "global_Macroalgae and Turf algae")

cat("::: {.figure #fig-x}\n")
cat(paste0("![](", fig2a,"){width=400px}\n\n"))
cat(paste0("Modelled temporal trend in Macroalgae (green
  ribbon with white line) and Turf algae (blue ribbon with white line)  
  for the Global scale.  The green and blue bands represent
  80% and 95% (darker) credibility intervals.  Grey ribbon represents 
  years for which there are no observed data.\n"))
cat(":::\n\n")
```
     